LSOA domestic Electricty and Gas maps

### 2021-09-03 LSOA Fuel poverty.Rmd
Adding Fuel poverty against deprevation graphs

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton")
#Around Bargate and Freemantle increased fuel poverty
```
```{r Portsmouth LSOA Fuel Pov 2012 2018}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
#Charles Dickens increased fuel poverty
```
```{r Winchester LSOA Fuel Pov 2012 2018}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
#head(census_age) lots of variables
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```

## 2012 Fuel poverty & Census 2011 data

```{r Plotting the 2012 fuel poverty vs 2011 percent over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
fp_LSOA_2012_df$LSOA11CD <- fp_LSOA_2012_df$`LSOA Code`
Census_age_2012fp <- merge(fp_LSOA_2012_df, census_age, by = "LSOA11CD")
# select the variables we want for clarity
df_2012 <- dplyr::select(Census_age_2012fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65", prop_65m)
head(df_2012)
# table(df$`LA Name`)
df_2012$la_name <- df_2012$`LA Name` # make a new variable with an easier name
df_2012$pcFuelPoor <- df_2012$`Proportion of households fuel poor (%)` # same - this is actually a % not a proportion!
# select the places we want here
getSolent <- function(df){
  # assumes we are filtering on la_name
  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
                           la_name == "East Hampshire"|
                           la_name == "Eastleigh"|
                           la_name == "Fareham"|
                           la_name == "Gosport"|
                           la_name == "Hart"|
                           la_name == "Havant"|
                           la_name == "New Forest"|
                           la_name == "Portsmouth"|
                           la_name == "Rushmoor"|
                           la_name == "Southampton"|
                           la_name == "Test Valley"|
                           la_name == "Winchester"|
                           la_name == "Isle of Wight"
                           )
  return(res)
}
Solent_2012 <- getSolent(df_2012) # use our function to get just Solent LAs
nrow(Solent_2012)
ggplot(Solent_2012, aes(x= 100 * prop_65m, 
                   y= pcFuelPoor, 
                   colour = la_name)) + # use colour for each LA
  geom_point() +
  geom_smooth() + # adds a smoothed best fit line
  theme(legend.position = "None") + # otherwise we get the colour legend at the side
  labs(x = "% aged > 65, 2011 Census",
       y = "% households in fuel poverty, 2012") +
  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
message("Correlation coeficient across al LSOAs (2012)")
cor(Solent_2012$prop_65m, Solent_2012$pcFuelPoor)
```

## 2019 Fuel poverty & Census 2011 data

```{r Plotting the 2019 fuel poverty vs 2011 percent over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
Census_age_2019fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
names(Census_age_2019fp)
# select the variables we want for clarity
df_2019 <- dplyr::select(Census_age_2019fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65", prop_65m)
head(df_2019)
# table(df$`LA Name`)
df_2019$la_name <- df_2019$`LA Name` # make a new variable with an easier name
df_2019$pcFuelPoor <- df_2019$`Proportion of households fuel poor (%)` # same - this is actually a % not a proportion!
# select the places we want here
Solent_2019 <- getSolent(df_2019) # use our function to get just Solent LAs
nrow(Solent_2019)
ggplot(Solent_2019, aes(x= 100 * prop_65m, 
                   y= pcFuelPoor, 
                   colour = la_name)) + # use colour for each LA
  geom_point() +
  geom_smooth() + # adds a smoothed best fit line
  theme(legend.position = "None") + # otherwise we get the colour legend at the side
  labs(x = "% aged > 65, 2011 Census",
       y = "% households in fuel poverty, 2019") +
  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
message("Correlation coeficient across al LSOAs (2019)")
cor(Solent_2019$prop_65m, Solent_2019$pcFuelPoor)
```

>>>>

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = fp_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton")
#Around Bargate and Freemantle increased fuel poverty
```
```{r Portsmouth LSOA Fuel Pov 2012 2018}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = fp_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
#Charles Dickens increased fuel poverty
```
```{r Winchester LSOA Fuel Pov 2012 2018}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = fp_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Linking age and Fuel Poverty
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```

## 2012 Fuel Poverty & Census 2011 Data
```{r Plotting the fuel poverty in over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
fp_LSOA_2012_df$LSOA11CD <- fp_LSOA_2012_df$`LSOA Code`
Census_age_2012fp <- merge(fp_LSOA_2012_df, census_age, by = "LSOA11CD")
# select the variables we want for clarity
df_2012 <- dplyr::select(Census_age_2012fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65", prop_65m)
head(df_2012)
# table(df$`LA Name`)
df_2012$la_name <- df_2012$`LA Name` # make a new variable with an easier name
df_2012$pcFuelPoor <- df_2012$`Proportion of households fuel poor (%)` # same - this is actually a % not a proportion!
# select the places we want here
getSolent <- function(df){
  # assumes we are filtering on la_name
  res <- dplyr::filter(df, la_name == "Basingstoke and Deane"|
                           la_name == "East Hampshire"|
                           la_name == "Eastleigh"|
                           la_name == "Fareham"|
                           la_name == "Gosport"|
                           la_name == "Hart"|
                           la_name == "Havant"|
                           la_name == "New Forest"|
                           la_name == "Portsmouth"|
                           la_name == "Rushmoor"|
                           la_name == "Southampton"|
                           la_name == "Test Valley"|
                           la_name == "Winchester"|
                           la_name == "Isle of Wight"
                           )
return(res)
}
Solent_2012 <- getSolent(df_2012) # use our function to get just Solent LAs
nrow(Solent_2012)
ggplot(Solent_2012, aes(x= 100 * prop_65m, 
                   y= pcFuelPoor, 
                   colour = la_name)) + # use colour for each LA
  geom_point() +
  geom_smooth() + # adds a smoothed best fit line
  theme(legend.position = "None") + # otherwise we get the colour legend at the side
  labs(x = "% aged > 65, 2011 Census",
       y = "% households in fuel poverty, 2012") +
  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
message("Correlation coeficient across al LSOAs (2012)")
cor(Solent_2012$prop_65m, Solent_2012$pcFuelPoor)

```
##2019 Fuel Poverty & Census 2011 data
```{r Plotting the 2019 fuel poverty vs 2011 percent over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
Census_age_2019fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
names(Census_age_2019fp)
# select the variables we want for clarity
df_2019 <- dplyr::select(Census_age_2019fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65", prop_65m)
head(df_2019)
# table(df$`LA Name`)
df_2019$la_name <- df_2019$`LA Name` # make a new variable with an easier name
df_2019$pcFuelPoor <- df_2019$`Proportion of households fuel poor (%)` # same - this is actually a % not a proportion!
# select the places we want here
Solent_2019 <- getSolent(df_2019) # use our function to get just Solent LAs
nrow(Solent_2019)
ggplot(Solent_2019, aes(x= 100 * prop_65m, 
                   y= pcFuelPoor, 
                   colour = la_name)) + # use colour for each LA
  geom_point() +
  geom_smooth() + # adds a smoothed best fit line
  theme(legend.position = "None") + # otherwise we get the colour legend at the side
  labs(x = "% aged > 65, 2011 Census",
       y = "% households in fuel poverty, 2019") +
  facet_wrap(. ~ la_name) # draws a separate plot for each LA (in a different colour)
message("Correlation coeficient across al LSOAs (2019)")
cor(Solent_2019$prop_65m, Solent_2019$pcFuelPoor)
```

####Plotting Fuel Poverty Against Deprevation
```{r plotting Change in Fuel Pov against dep}
LSOAfuelpovdep <- merge(lsoa_fuelpov20122018, LSOAdep, by= "LSOA11CD")
names(LSOAfuelpovdep)
df <- dplyr::select(LSOAfuelpovdep, LSOA11CD, "LA Name.x", fp_diff, IMDScore, fp2012, IMD_Decile, fp2018
)

head(df)
Solent <- dplyr::filter(df, `LA Name.x` == "Basingstoke and Deane"|
                           `LA Name.x` == "East Hampshire"|
                           `LA Name.x` == "Eastleigh"|
                           `LA Name.x` == "Fareham"|
                           `LA Name.x` == "Gosport"|
                           `LA Name.x` == "Hart"|
                           `LA Name.x` == "Havant"|
                           `LA Name.x` == "New Forest"|
                           `LA Name.x` == "Portsmouth"|
                           `LA Name.x` == "Rushmoor"|
                           `LA Name.x` == "Southampton"|
                           `LA Name.x` == "Test Valley"|
                           `LA Name.x` == "Winchester"|
                           `LA Name.x` == "Isle of Wight"
                           )
head(Solent)
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(fp_diff/fp2012), 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "% Change in Fuel Poverty")
```
Try adding facets for each Local Authority

```{r addFacetsToFuelpovdep}
# or without colour but using facets for Local Authorities
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(fp_diff/fp2012), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change Fuel Poverty") +
  facet_wrap(`LA Name.x` ~ .)

nrow(Solent)
```

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
Adding Fuel poverty against deprevation graphs

```{r plotting change in elec usage against dep}
LSOAdepelec <- merge(merged_de, LSOAdep, by= "LSOA11CD")
names(LSOAdepelec)
df <- dplyr::select(LSOAdepelec, LSOA11CD, "Local Authority Name.x", "de_diff", IMDScore, de2010, IMD_Decile
)

@@

nrow(Solent)
```
####Map with Overlay 
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)

@@

nrow(Solent)
```
####Map with overlay 
```{r Check leaflet for change i dom gas consumption}
library(leaflet)

>>>>

```{r plotting change in elec usage against dep}
LSOAdepelec <- merge(merged_de, LSOAdep, by= "LSOA11CD")
names(LSOAdepelec)
df <- dplyr::select(LSOAdepelec, LSOA11CD, "Local Authority Name.x", "de_diff", IMDScore, de2010, IMD_Decile, de2019
)

@@

nrow(Solent)
```
####Plotting the relationship between Electricty consumption and deprevation
```{r plotting electricty consumption against deprevation}
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =de2019, 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "Electricity Consumption")
```
```{r addFacetsToElecconsumption}
# or without colour but using facets for Local Authorities
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =de2019, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Electricty Consumption") +
  facet_wrap(`Local Authority Name.x` ~ .)

nrow(Solent)
```

####Map with Overlay 
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)

@@

nrow(Solent)
```
####Map with overlay 
```{r Check leaflet for change in dom gas consumption}
library(leaflet)
